---
title: Jaime Andrés Arau Pontones
output:
  html_document:
    css: www/cv.css
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
## load packages
source("1.Code/00_set_up.R")

## text for CV

source("1.Code/05_text_for_CV.R")


```

<head>

  <style>
      <link href="https://fonts.googleapis.com/css2?family=Roboto&display=swap" rel="stylesheet">
  </style>
</head>


<p style = "text-align: center;">
`r txt_website` <br>
`r txt_address`  | <img class = "icon_intro" src = "4.imgs/phone.png"> `r txt_phone` | <img class = "icon_intro" src = "4.imgs/email.png"> `r txt_email` 
</p>


<p style = "font-weight: bold;">

Economist with `r txt_years_of_experience`+ years of experience in data science and MEL. I specialize in using data science to improve learning and accountability in development programs. My expertise includes data analysis, dashboard development, global data collection initiatives, and capacity-building. I have successfully led over `r txt_number_projects` projects in `r txt_number_countries` countries, demonstrating my ability to navigate diverse contexts and deliver impactful results through the effective use of data-driven insights.
</p>

 

<img src = "4.imgs/globe.png" class = "icon_header icon_big"> <h1 class="header_section"> INTERNATIONAL EXPERIENCE </h1>


`r knitr::combine_words(txt_countries)`.



<img src ="4.imgs/education.png" class = "icon_header icon_big">  <h1 class="header_section"> EDUCATION </h1>


<table>
  <tr>
    <td> **MSc. In Economic Development and Growth |** Lund University and Carlos III de Madrid	 </td>
    <td class = "col_period"> 2012 - 2014 </td>
  </tr>
  
  <tr>
  <td> **B.A. Honours in Economics with a minor in Global Studies |** University of Ottawa  </td>
  <td class = "col_period"> 2005 - 2009</td>
  </tr>
  
</table>


<img src ="4.imgs/skills.png" class = "icon_header"> <h1 class="header_section"> PERSONAL SKILLS AND COMPETENCIES </h1>


<table class = "skills">
  <tr>
    <td class = "col_skills"> Languages </td>
    <td> `r txt_languages` </td>
  </tr>
  
  <tr>
    <td> Software & Systems</td>
    <td> `r knitr::combine_words(txt_software)` </td>
  </tr>
</table>


<img src ="4.imgs/experience.png" class = "icon_header"> <h1 class="header_section"> PROFESSIONAL EXPERIENCE </h1>

<table>


<tr>
  <td>**Independent Data Scientist**</td>
  <td class ="col_period" >2019 - now</td>
</tr>

<tr>
<td>
* Design monitoring and evaluation frameworks;
* Develop data collection strategies to efficiently inform MEL systems;
* Design frameworks and digital systems to monitor large development programs;
* Advise on survey and data collection implementation globally;
* Build local capacity to robustly collect and analyze data.
</td>
</tr>

<tr>
  <td>**Survey and Data Specialist | Oxford Policy Management.** Oxford, UK</td>
  <td class ="col_period" >2015 - 2019</td>
</tr>

<tr>
<td>
* Design and implementation of large data collection exercises internationally; 
* Development of system and real time dashboards for Data Quality Assurance of household surveys; 
* Questionnaire design and CAPI programming.

</td>
</tr>


<tr>
  <td>**Project Manager | C-230 CONSULTORES / FUNDACIÓN IDEA.** Mexico City, Mexico</td>
  <td class ="col_period" >2014 - 2015</td>
</tr>

<tr>
<td>
*	Evaluation design and econometric data analysis; 
*	Training and management of fieldwork teams for data collection exercises.
</td>
</tr>


<tr>
  <td>**Summer Intern. Gender diversity unit | INTER-AMERICAN DEVELOPMENT BANK.** Washington D.C</td>
  <td class ="col_period" >2013</td>
</tr>

<tr>
<td>
*	Evaluation design and econometric data analysis.
</td>
</tr>


<tr>
  <td>**Monitoring and Evaluation Officer | THE HUNGER PROJECT.** Mexico City, Mexico</td>
  <td class ="col_period" >2009 - 2012</td>
</tr>

<tr>
<td>
*	Design and implementation of MEL Systems; and
*	Design, implementation, and analysis of Participatory Rural Appraisals.

</td>
</tr>


<tr>
  <td>**Consultant | ASHOKA MÉXICO & CENTRAL AMERICA.** Mexico City, Mexico</td>
  <td class ="col_period" >2010 - 2011</td>
</tr>

<tr>
<td>
*	Evaluation design; and
* Training and management of fieldwork teams for data collection exercises


</td>
</tr>

</table>

<div class = "page_break"> </div>

<img src ="4.imgs/projects.png" class = "icon_header"> <h1 class="header_section"> PROJECTS WHICH BEST ILLUSTRATE MY SKILLS AND COMPETENCIES </h1>

`r txt_projects`
<!-- Write your comments here 
<table id = "table_projects">
`r txt_projects`
</table>

-->

```{r echo=FALSE, warning=FALSE}
#pagedown::chrome_print("template.html", "template3.pdf")
```


<img src ="4.imgs/conference.png" class = "icon_header"> <h1 class="header_section"> CONFERENCES AND SEMINARS </h1>

<table>

<tr>
  <td>**European Commission & Government of Cuba** | Havana, Cuba</td>
  <td class ="col_period" >2014 - 2015</td>
</tr>

<tr>
<td>
Lecturer at Seminar on Impact Evaluation
</td>
</tr>
</table>

<img src ="4.imgs/fellowship.png" class = "icon_header"> <h1 class="header_section"> FELLOWSHIPS AND ADDITIONAL INFORMATION </h1>

<table>

<tr>
  <td>European Commission Erasmus Mundus Fellowship</td>
  <td class ="col_period" >2012 - 2014</td>
</tr>


</table>